---
title: "Lab meeting 1"
author: "Brendan Palmer"
date: "19th June 2019"
output: slidy_presentation
---

# Data overview

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#Packages 

library(tidyverse)
library(png)
library(grid)
library(beeswarm)

```

- Analysis of a data set provided by Dr Aoife Coffee, UCC Library
- This experiment assessed the impact of UV over 21 days on plant growth and the accumulation of secondary metabolites
- Three varieties of lettuce
    - Cos Dixter, Skyphos, Red Oakleaf
    
- Three filter types employed
    - ca, my, ptp
    
- Plant samples taken at 0, 1, 2 and 3 weeks
    - For the first 7 days, no filter used
    - Plants were sampled without replacement
        - Same baseline used for each filter
        
# Questions to ask of the data

- $H_{o}$: $\mu_{red}$ = $\mu_{cos}$ = $\mu_{sky}$
    - Mean falvonoid content of lettuce varieties is the same

- $H_{o}$: $\mu_{ca}$ = $\mu_{ptp}B$ = $\mu_{my}$
    - Mean flavonoid content of lettuce grown under different filters is the same

# Initial analysis

```{r fig.width=8, fig.height=4,echo=FALSE}

img <- readPNG("plots/2019-06-17_overview1_flavonoids.png")
 grid.raster(img)
 
```

# Initial analysis

```{r fig.width=8, fig.height=4,echo=FALSE}
img <- readPNG("plots/2019-06-18_overview2_flavonoids.png")
 grid.raster(img)
```

# Initial analysis

```{r fig.width=8, fig.height=4,echo=FALSE}
img <- readPNG("plots/2019-06-18_biomass_overview.png")
 grid.raster(img)
```

# Summary

- Relatively little change in flavonoid content during the first two weeks
- Spike in flavonoid content at week 3
- Cos Dixter flavonoid (ppm) content was highest of all three varieties
- Filter type had visiable impact on biomass
    - ptp > my > ca